Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-26 paper/paper.Rmd
Pandoc list fail...
First batch revisions

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.

@@

We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study. In four cases, we powered the replication attempt to 80\% post-hoc power. In four cases, we used the original sample size. In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

@@

+ every student a separate project
+ group projects
+ single class projects

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to this non-probability sample.  This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.

@@

@@

We

Contacting original authors

@@

>>>>

Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. Yet under the current incentive structure for science, replication is not typically valued replication is not typically valued for publication [@makel2012], or in metrics of research productivity [@koole2012]. One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012]. Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.

@@

We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study. In four cases, we powered the replication attempt to 80\% power based on post-hoc power calculations of the original effect sizes. In four cases, we used the original sample size. In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

@@

every student a separate project
group projects
single class projects

@@

Students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to this non-probability sample.  This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.

@@

As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.  Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.

@@

**Add our own paragraph and IRB notes**

We are not familiar with the particularities of Institutional Review Boards across institutions, but suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.  We briefly highlight a few, with potential resolutions and comments.

*IRB approval is not possible within the time constraints of a class.*  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds. Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if said studies provide full open-source materials that can be used in the IRB protocol submitted.

*There is a potential for harm given constraints of class.* Instructor review. Has been previously approved, and coercion/privacy confidentiality. Anonymizing codes; securing data. How much role instructors play in this dependent on student competence.

@@

## Funding and Power limitations

(Eric -I think this should be addressed - maybe mention free participant pools, value of learning how to recruit. OR if lucky (like us) apply for a grant.  Also call for OSF and other organizations devoted to replications to provide small grants of this sort.

Case-by-case selection
